Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Lemmas.tex
resolving edits

More generally, for any set of types $A$, the expected number of times that 
an agent with a type in $A$ appears in a phase $s$ is at most 
$f(A) \cdot \ARMNUM \cdot \log(s)$,
where $f(A) := \Prob[\AgV \sim \AgentDist]{\dkedit{\AgV} \in A}$.
\end{rlemma}

@@

Fix a phase $s$, and let $S_t$ be the set of arms that have been
pulled at most $s$ times by time $t$.
Let $\tau_m$ be the maximum of $t_s$ (the start of phase $s$)
and the time $t$ when $S_t$ first contains \dkedit{(at most)} $m$ elements.
The phase ends when $S_t$ contains no elements, i.e., $\tau_0 = t_{s+1}$.
We consider the expected number of pulls during times
$\dkedit{t \in} [\tau_m, \tau_{m-1})$ made by agents whose types are in $A$.

>>>>

More generally, for any set of types $A$, the expected number of times that 
an agent with a type in $A$ appears in a phase $s$ is at most 
$f(A) \cdot \ARMNUM \cdot \log(s)$,
where $f(A) := \Prob[\AgV \sim \AgentDist]{\AgV \in A}$.
\end{rlemma}

@@

Fix a phase $s$, and let $S_t$ be the set of arms that have been
pulled at most $s$ times by time $t$.
Let $\tau_m$ be the maximum of $t_s$ (the start of phase $s$)
and the time $t$ when $S_t$ first contains (at most) $m$ elements.
The phase ends when $S_t$ contains no elements, i.e., $\tau_0 = t_{s+1}$.
We consider the expected number of pulls during times
$t \in [\tau_m, \tau_{m-1})$ made by agents whose types are in $A$.
